\chapter{August - 2012} % Chapter title
\label{ch:aug:2012} % For referencing the chapter elsewhere, use \autoref{ch:introduction} 

%----------------------------------------------------------------------------------------

\section{Reading, Take a step back}
In the past years, Aaron Swartz was the decider, tasked with making the best selection from the options life presented.
He could play with this friend or that one, go to this college or that one, take this job offer or the other one.

Instead of just picking the best option, Aaron try to invent new ones. Instead of just avoiding the stuff that bugs him, should he start making plans to fix them.

It is a big change for him psychologically, which influence me much more. I see the positive and active attitude of his facing tough life from the article. Just as he said, he is charting his destiny, instead of following some track. 


\url{http://www.aaronsw.com/weblog/stepback}
\hfill {\tiny  edited on 2012-08-20.}

\section{Reading, Batman Begins}
The article written by Aaron Swartz is about the movie "batman". He told us briefly the story about the history of Batman. In practice, the history is how the two sides, organized criminal groups and the rich, keep their power balanced. The power hold by either of sides make all people, both the rich and the poor, suffer from the unbalanced world. Even if the rich who seems  on behalf of the positive side holds stronger power, the common people who live in the world will still suffer. It sounds ridiculous, which is true for us in the real world.
\hfill {\tiny  edited on 2012-08-24.}
